---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# shape2kml

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/shape2kml)](https://CRAN.R-project.org/package=shape2kml)
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
<!-- badges: end -->

# Geospatial Polygons to DJI compatible KML (shape2kml)
The **shape2kml** package serves a importnat purpose: converting (multi)polygon data into a KML format that is compatible with DJI drones. While **KML** or **KMZ** files exported from popular GIS Software like ArcGIS (ESRI), QGIS (QGIS Development Team), or R (R Core Team) may not be directly compatible with DJI drones, this package bridges that gap.

When preparing flight plans for small Unmanned Aerial Vehicles (sUAVs), manually digitizing polygons using Google Earth Pro (GEP) to ensure compatibility with DJI's pilot app can be tedious. This function streamlines the process, making it significantly more efficient.

The **shape2kml** can process any polygon data readable by the sf package, providing flexibility in data sources. However, at this time, only following file types are tested and are supported; they are types include feature classes (ESRI), shapefiles (ESRI), GeoJSON (OGC), and KML (Google). Users can seamlessly convert spatial data from various formats into DJI-compatible KML files, empowering smoother flight planning and execution for drone operations.
## Installation

You can install the development version of shape2kml from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("suvedimukti/shape2kml")
```

## Load required packages

The package has three different data types

```{r example}
library(shape2kml)
library(sf)
```

## List data types: shape2kml package

```{r datatypes}
# Once the package is installed, we can use system.file to locate the 
# data ".inst/testdata" that come with the package

sys_dat_path <- system.file("testdata", package = "shape2kml")

# list shape file (there is only one shapefile)
test_shp <- list.files(sys_dat_path, pattern = "\\.shp$", full.names = TRUE)

## list all data types
all_data <- list.files(sys_dat_path, full.names = FALSE)
```

## Read and plot example data


```{r plot data}
shp_dat = sf::st_read(test_shp)

#Plot
library(ggplot2)
gp<- ggplot2::ggplot()+
  ggplot2::geom_sf(data = shp_dat)
gp
```

## Convert data to DJI compatible kml file

```{r, poly2kml}
# lets convert all data types that can be read by `sf::st_read`
shape2kml::convert_polygon2_kml(input_dir = test_shp,output_dir = "",name_field = "tile_id",desc_field = "",recursive = FALSE)


```
